Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-08 src/tex/ms.tex
Finish likelihood part

\begin{align}
    \log{\mathcal{L}(d|\theta)} = -\left<d-h(\mathbf{\theta})|d-h(\mathbf{\theta})\right>/2,
\label{eq: loglikelihood}
\end{align}
where $d$ is the strain data, $h(\mathbf{\theta})$ is the strain predicted by a
waveform model with a specific set of source parameters. The right handside of
eq. \ref{eq: loglikelihood} can be evaluated in either time or frequency domain.
Since it is computationally cheaper to compute the likelihood in the frequency
domain, we choose to compute the likleihood throughout this work, which can be defined as 
\begin{align}
    \left<a|b\right> = 4 Re\int \frac{a^*(f)b(f)}{\mathcal{S}_n(f)} df,
\label{eq: innerproduct}
\end{align}
where $\mathcal{S}_n(f)$ is the noise power spectral density (PSD). To compute
the integral shown in eq. \ref{eq: innerproduct}, we need to evaluate a chosen
waveform model $h(\mathbf{\theta})$ at a number of frequnecy sample points.
Evaluting the likelihood function is often the most computationally intensive
part of the PE. The most accurate waveform model is numerical relativity (NR).
However, depending on the source parameters, generating one time series of
strain using can takes a day to half a year, which makes NR prohibitably
expensive for PE. To circumvent this problem, there are a number of waveform
"approximant" families, including the IMRPhenom family \kw{}, SEOB family \kw{},
and NR surrogate family\kw{cite}. For shorter event such as a $30-30\ M_{\odot}$
BBH, one waveform call could take $10\text{ms}$ to $\sim 1s$ \kw{verify number
in lalsuite}. For longer event such as a $1.4-1.4\ M_{\odot}$ BNS event, the
evaluation time could go up to \kw{Fill}.

@@

\kw{Talks about implication}
\begin{enumerate}
    \item Multi-modality in testing GR PE
    \item No pre-training, i.e. more adaptive to glitch and new noise model
    \item As gauruntee to converge as other MCMC method
    \item Access to higher dimensional problem
    \item Much lower computational cost, allow poor institute to just run PE on colab if they want.
\end{enumerate}

@@

% Higher dimensional problems
While standard GW analysis goes up to 17 dimensions. non-standard GW PE problems
can have more parameters, which could potentially lead to more complicate
geometry in the target posterior. For example,

\begin{enumerate}
    \item Multi-device scaling?
    \item Other detectors configuration
    \item Combining with noise inference
    \item Higher dimensional problems need HMC still
\end{enumerate}

>>>>

\begin{align}
    \log{\mathcal{L}(d|\theta)} = -\left<d-h(\mathbf{\theta})|d-h(\mathbf{\theta})\right>/2,
\label{eq: loglikelihood}
\end{align}
where $d$ is the strain data, $h(\mathbf{\theta})$ is the strain predicted by a
waveform model with a specific set of source parameters. The right handside of
eq. \ref{eq: loglikelihood} can be evaluated in either time or frequency domain.
Since it is computationally cheaper to compute the likelihood in the frequency
domain, we choose to compute the likleihood throughout this work, which can be defined as 
\begin{align}
    \left<a|b\right> = 4 Re\int \frac{a^*(f)b(f)}{\mathcal{S}_n(f)} df,
\label{eq: innerproduct}
\end{align}
where $\mathcal{S}_n(f)$ is the noise power spectral density (PSD). To compute
the integral shown in eq. \ref{eq: innerproduct}, we need to evaluate a chosen
waveform model $h(\mathbf{\theta})$ at a number of frequnecy sample points.
Evaluting the likelihood function is often the most computationally intensive
part of the PE. The most accurate waveform model is numerical relativity (NR).
However, depending on the source parameters, generating one time series of
strain using can takes a day to half a year, which makes NR prohibitably
expensive for PE. To circumvent this problem, there are a number of waveform
"approximant" families, including the IMRPhenom family \kw{}, SEOB family \kw{},
and NR surrogate family\kw{cite}. For shorter event such as a $30-30\ M_{\odot}$
BBH, one waveform call could take $10\text{ms}$ to $\sim 1s$ \kw{verify number
in lalsuite}. For longer event such as a $1.4-1.4\ M_{\odot}$ BNS event, the
evaluation time could go up to \kw{Fill}. Since one needs to evaluate the
likelihood many times during sampling\footnote{A typical PE run with
\texttt{Bilby} takes $>10^6$ likelihood evalutation to converge.}, the
computational cost in evaluating the waveform accumulate and is the main reason
of the long runtime of GW PE.

@@

% Multi-modality in testing GR PE

% Access to higher dimensional problem
While standard GW analysis goes up to 17 dimensions. non-standard GW PE problems
can have more parameters, which could potentially lead to more complicate
geometry in the target posterior. For example,

@@

% Multi-device scaling

% Other detectors configuration

% Higher dimensional problems need HMC still
